Material Methods

### 2019-09-26 doc/MatMeth.Rmd
night notes

Statistical analysis was performed in R (v3.5.2)[@Rstudio].

The distributions of CO counts per cell was assessed for normailty (supplemental figure). Mouse mean MLH1 count was used to get around the bad discreet nature of count data. (normality was confirmed with X distribution, supplemental figure).

framework for analyzing the MLH1 patterns
1. write equation

$X \sim mouse average MLH1 ~ sex + subspecies + random(strain) + \xi $
 can't get the equation in the right format. I think this breaks the pdf kniting.

@@

-specific R packages
-non-parametric  (tests and measures for dealing with count data)
-hypothesis tested (size, DSB number)

Comparison/analysis of variation in MLH1 counts within and between groups was done within a general linear/ mix model frame work, using X package (cite).
With X formula Co count ~ blah + blah, with random strain specific sex effect.

(we used this frame work as proxy for 'polymorphism' and 'divergence' in MLH1 counts across house mouse and closely related species.)

>>>>

0. discribe basic assesment and comparison of MLH1 means (and how it is proxy for genome wide recombination rates)
- assessment and treatment of data quality control ect (correlation measured X)

The distributions of CO counts per cell was assessed for normailty (supplemental figure). Mouse mean MLH1 count was used to get around the bad discreet nature of count data. (normality was confirmed with X distribution, supplemental figure). <re-write this dumb paragraph>

Statistical analysis was performed in R (v3.5.2)[@Rstudio]. mixed models use lmer4 package (cite)

1. framework for analyzing the MLH1 evolutionary patterns across mus species complex. (what is the main question we were tackling when designing this framework?)

2. write equation, discribe terms (proxies for within and between polymorphsm)
logic / choices for fixed and random effects

3. what are the 2 general / basic questions this framework can be applied to.

$X \sim mouse average MLH1 ~ sex + subspecies + random(strain) + \xi $
< can't get the equation in the right format. I think this breaks the pdf kniting.>

4. how can DMC1 measures be added to the mixed model

5. discriptions of mlh1 outside of framework (missing female data)

@@

Comparison/analysis of variation in MLH1 counts within and between groups was done within a general linear/ mix model frame work, using X package (cite).
(we used this frame work as proxy for 'polymorphism' and 'divergence' in MLH1 counts across house mouse and closely related species.)
